\articletitle{The Humble Bee}

\articleauthor{Ralph Waldo Emerson}
\begin{poem}
	\begin{stanza}
			Burly, dozing humble-bee,\verseline
			Where thou art is clime for me.\verseline
			Let them sail for Porto Rique,\verseline
			Far-off heats through seas to seek;\verseline
			I will follow thee alone,\verseline
			Thou animated torrid-zone!\verseline
			Zigzag steerer, desert cheerer,\verseline
			Let me chase thy waving lines;\verseline
			Keep me nearer, me thy hearer,\verseline
			Singing over shrubs and vines.
	\end{stanza}
	\begin{stanza}
			Insect lover of the sun,\verseline
			Joy of thy dominion!\verseline
			Sailor of the atmosphere;\verseline
			Swimmer through the waves of air;\verseline
			Voyager of light and noon;\verseline
			Epicurean of June;\verseline
			Wait, I prithee, till I come\verseline
			Within earshot of thy hum,--\verseline
			All without is martyrdom.
	\end{stanza}
	\begin{stanza}
			When the south wind, in May days,\verseline
			With a net of shining haze\verseline
			Silvers the horizon wall,\verseline
			And with softness touching all,\verseline
			Tints the human countenance\verseline
			With a color of romance,\verseline
			And infusing subtle heats,\verseline
			Turns the sod to violets,\verseline
			Thou, in sunny solitudes,\verseline
			Rover of the underwoods,\verseline
			The green silence dost displace\verseline
			With thy mellow, breezy bass.
	\end{stanza}
	\begin{stanza}
			Hot midsummer's petted crone,\verseline
			Sweet to me thy drowsy tone\verseline
			Tells of countless sunny hours,\verseline
			Long days, and solid banks of flowers;\verseline
			Of gulfs of sweetness without bound\verseline
			In Indian wildernesses found;\verseline
			Of Syrian peace, immortal leisure,\verseline
			Firmest cheer, and bird-like pleasure.
	\end{stanza}
	\begin{stanza}
			Aught unsavory or unclean\verseline
			Hath my insect never seen;\verseline
			But violets and bilberry bells,\verseline
			Maple-sap and daffodels,\verseline
			Grass with green flag half-mast high,\verseline
			Succory to match the sky,\verseline
			Columbine with horn of honey,\verseline
			Scented fern, and agrimony,\verseline
			Clover, catchfly, adder's-tongue\verseline
			And brier-roses, dwelt among;\verseline
			All beside was unknown waste,\verseline
			All was picture as he passed.
	\end{stanza}
	\begin{stanza}
			Wiser far than human seer,\verseline
			Yellow-breeched philosopher!\verseline
			Seeing only what is fair,\verseline
			Sipping only what is sweet,\verseline
			Thou dost mock at fate and care,\verseline
			Leave the chaff, and take the wheat.\verseline
			When the fierce northwestern blast\verseline
			Cools sea and land so far and fast,\verseline
			Thou already slumberest deep;\verseline
			Woe and want thou canst outsleep;\verseline
			Want and woe, which torture us,\verseline
			Thy sleep makes ridiculous.
	\end{stanza}
\end{poem}
\articlerights{Public Domain}