\articletitle{Give All To Love}

\articleauthor{Ralph Waldo Emerson}
\begin{poem}
	\begin{stanza}
			Give all to love;\verseline
			Obey thy heart;\verseline
			Friends, kindred, days,\verseline
			Estate, good-fame,\verseline
			Plans, credit and the Muse,--\verseline
			Nothing refuse.
	\end{stanza}
	\begin{stanza}
			'T is a brave master;\verseline
			Let it have scope:\verseline
			Follow it utterly,\verseline
			Hope beyond hope:\verseline
			High and more high\verseline
			It dives into noon,\verseline
			With wing unspent,\verseline
			Untold intent;\verseline
			But it is a god,\verseline
			Knows its own path\verseline
			And the outlets of the sky.
	\end{stanza}
	\begin{stanza}
			It was never for the mean;\verseline
			It requireth courage stout.\verseline
			Souls above doubt,\verseline
			Valor unbending,\verseline
			It will reward,--\verseline
			They shall return\verseline
			More than they were,\verseline
			And ever ascending.
	\end{stanza}
	\begin{stanza}
			Leave all for love;\verseline
			Yet, hear me, yet,\verseline
			One word more thy heart behoved,\verseline
			One pulse more of firm endeavor,--\verseline
			Keep thee to-day,\verseline
			To-morrow, forever,\verseline
			Free as an Arab\verseline
			Of thy beloved.
	\end{stanza}
	\begin{stanza}
			Cling with life to the maid;\verseline
			But when the surprise,\verseline
			First vague shadow of surmise\verseline
			Flits across her bosom young,\verseline
			Of a joy apart from thee,\verseline
			Free be she, fancy-free;\verseline
			Nor thou detain her vesture's hem,\verseline
			Nor the palest rose she flung\verseline
			From her summer diadem.
	\end{stanza}
	\begin{stanza}
			Though thou loved her as thyself,\verseline
			As a self of purer clay,\verseline
			Though her parting dims the day,\verseline
			Stealing grace from all alive;\verseline
			Heartily know,\verseline
			When half-gods go.\verseline
			The gods arrive.
	\end{stanza}
\end{poem}
\articlerights{Public Domain}