\daxiincontent{A Statement of Principles}{i dunno}

\articletitle{A Statement of Principles}

\articleauthor{i dunno}

\begin{enumerate}
	\item We want to live in a place guided by empathy, respect, justice, generosity, courage, fun and love.
	\item We want to live in a place governed by judgements that are honestly made, supported by evidence, accountable and transparent.
	\item We want to live in a place in which everyone’s needs are met, without harming the living world or the prosperity of future generations.
	\item We want to live in a place in which the fruits of the work we do and the resources we use are fairly and widely distributed, in which shared prosperity is a general project, and the purpose of economic life is to enable universal well-being.
	\item We want to live in a place in which all people have equal rights, in practice as well as in theory.
	\item We want to live in a place in which all people can feel secure, confident, safe and cared for.
	\item We want to live in a place in which, regardless of where they were born, everyone has a neighbourhood of which they feel proud, where they can freely participate in the life of the community.
	\item We want to live in a place which, proudly and consistently, supports people in need of help, including those fleeing from danger and persecution abroad.
	\item We want to live in a place in which a thriving natural world provides a refuge both for rich and abundant wildlife and for people seeking relief from the clamour of daily life.
	\item We want to live in a place whose political system is fair and fully representative, in which everyone has a voice and every vote counts, and whose outcomes can neither be bought nor otherwise engineered.
	\item We want to live in a place in which decisions are taken at the most appropriate level, to enhance democratic participation and connection.
	\item We want to live in a place in which everyone has access to the information needed to make meaningful democratic choices, and in which political debate is honest, accessible and inclusive.
	\item We want to live in a place in which education is a joyful process, encouraging children of all abilities to engage with enthusiasm, and adults to continue learning throughout their lives.
	\item We want to live in a place in which good housing, fast and effective healthcare and a healthy, sufficient diet are available to everyone.
	\item We want to live in a place that helps to build a safe, prosperous and resilient community of nations.
	\item We want to live in a place that is open to new ideas and information, and that values creativity, research and discovery.
\end{enumerate}

\articlerights{Copyright}